Lake Photic Zone Temperature accross the Conterminous United States

### 2019-07-30 manuscript/manuscript.Rmd
edits to figure and model code

>>>>

Using the 2007 and 2012 NLA data, we have successfully built a simple yet robust model of lake surface temperature for the conterminous United States.  Average ambient air temperature from the sample date, data obtained from the PrRISM Climate Group, was the most important variable imapcting the final model's accuracy.
